---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DSPG

<!-- badges: start -->
<!-- badges: end -->

The goal of the DSPG package is to provide access to commonly used publicly available data for the DSPG projects at ISU.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSPG-ISU/DSPG")
```

The above code might not work as supposed to because the repo is private. If the installation fails with an error along the lines that the repo doesn't exist, make sure to clone the repo onto your machine. Unzip the folder. Open `DSPG.Rpoj` in RStudio (by double-clicking the file). Install the package using the command

``` r
# install.packages("devtools")
devtools::install()
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(DSPG)
```

All of the data sets have an extensive example section with code that should help you get started. 

## Content

The datasets available are 

```{r, echo=FALSE}
cat(gsub(".rda","", dir("data")))
```

Check each file with the R help, e.g. `?ia_cities`, for more details.

## How to contribute

This repository is organized in form of an R package. 
The structure of folders and files is sensitive, so be sure to first read the following instructions before you make any changes to them.
